Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-08 paper/galsize_paper.tex
edited intro, added some of the relevant references on size-Rvir connection and on early AM.

Many properties of observed galaxies exhibit remarkably tight scaling relations. Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}. Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}. Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}. In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy $\mstar$ and $\rhalf$ to the properties of the galaxy's parent dark matter halo.

>>>>

Many properties of observed galaxies exhibit remarkably tight scaling relations. Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.

Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}. More recently, connection of galaxy sizes to virial radius of their parent halos have been 
explored by converting stellar mass to halo mass and virial radius, using abundance matching \citep{kravtsov_etal04,tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,conroy_etal06}.  Such analysis indicated that sizes of galaxies
are, on average, proportional to the virial radii of their host halos, both at $z=0$ \citep{kravtsov13}, and higher redshifts \citep{huang_etal17,somerville_etal17}.

Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}. In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar masses and sizes to the properties of the galaxy's parent dark matter halo.
